Consensus Problems in Networks of Agents\\ with Switching Topology and Time-Delays

### 2020-10-26 Paper.tex
Complete Chapter 4 & Change EN Words Color

\geometry{a4paper,scale=0.8}
\geometry{a4paper,left=3.18cm,right=3.18cm,top=2.54cm,bottom=2.54cm}
\linespread{1.5}

@@

\begin{abstract}
In this paper, we discuss consensus problems for a network of dynamic agents with ﬁxed and switching topologies. 
We analyze three cases: i) networks with switching topology and no time-delays, ii) networks with ﬁxed topology and communication time-delays, and iii) max-consensus problems (or leader determination) for groups of discrete-time agents. 
In each case, we introduce a linear/nonlinear consensus protocol and provide convergence analysis for the proposed distributed algorithm. 
Moreover, we establish a connection between the Fiedler eigenvalue of the information ﬂow in a network (i.e. algebraic connectivity of the network) and the negotiation speed (or performance) of the corresponding agreement protocol. 
It turns out that balanced digraphs play an important role in addressing average-consensus problems. 
We introduce disagreement functions that play the role of Lyapunov functions in convergence analysis of consensus protocols. 
A distinctive feature of this work is to address consensus problems for networks with directed information ﬂow. 
We provide analytical tools that rely on algebraic graph theory, matrix theory, and control theory. 
Simulations are provided that demonstrate the eﬀectiveness of our theoretical results.

@@

\section{Introduction}
Distributed decision-making for coordination of networks of dynamic agents has attracted several researchers in recent years. 
This is partly due to broad applications of multi-agent systems in many areas including cooperative control of unmanned air vehicles (UAVs), ﬂocking of birds [22, 24, 23], schooling for underwater vehicles, distributed sensory networks, attitude alignment of clusters of satellites, and congestion control in communication networks [21].

@@

Agreement problems have a long history in the ﬁeld of computer science, particularly in automata theory and distributed computation [15]. 
In many applications involving multiagent/multi-vehicle systems, groups of agents need to agree upon certain quantities of {\color{green}interest}. 
Such quantities might or might not be related to the motion of the individual agents. 
As a result, it is important to address agreement problems in their general form for networks of dynamic agents with directed information ﬂow under link failure and creation (i.e. variable network topology).

@@

Our main contribution in this paper is to deﬁne and address consensus problems under a variety of assumptions on the network topology (being ﬁxed or variable), presence or lack of communication time-delays, and boundedness of the inputs of dynamic agents. 
In each case, we provide convergence analysis and for linear protocols establish direct connections between performance and robustness of a consensus protocol and the properties of graph Laplacian of the information ﬂow in the network.

@@

In the past, a number of researchers have worked in problems that are essentially diﬀerent forms of agreement problems with diﬀerences regarding the types of agent dynamics, the properties of the graphs, and {\color{green}the names of the tasks of interest}. 
In [25, 7, 6], graph Laplacians are used for the task of formation stabilization for groups of agents with linear dynamics. 
Their method for formation stabilization has not yet been extended to systems with nonlinear dynamics that are not feedback linearizable. 
Special cases of this approach are known as leader-follower type architectures and have been widely used by numerous researchers [19, 4, 14]. 
In [18], graph Laplacians are used in the context of dynamic graph theory. 
In [24, 23], {\color{green}ﬂocking and heading angle} alignment for multiple particles is analyzed from the point of view of statistical mechanics and a phase transition phenomenon is observed that occurs the information ﬂow in the network becomes connected. 
The work in [13] focuses on attitude alignment for undirected graphs in which the agents have simple dynamics motivated by the model used in [24]. 
It is claimed that the connectivity of the graph on average is suﬃcient for convergence of the heading angles of the agents. 
In [20], the authors addressed convergence of linear and nonlinear protocols for networks with undirected graphs in presence or lack of communication time-delays. 
Theoretically, analyzing consensus on directed graphs is more challenging and is considered in the present paper.

@@

In this paper, we provide convergence analysis of consensus protocol for a network of {\color{green}integrators} with a directed information ﬂow and ﬁxed or switching topology. 
Our analysis relies on several tools from algebraic graph theory [1, 11] and matrix theory [12]. 
We establish a connection between the performance of the linear consensus protocol and the Fiedler eigenvalue of graph Laplacian of a graph called the mirror graph (that is closely-related to the original directed graph).

@@

It turns out that a class of directed graphs called balanced graphs have a crucial role in derivation of an invariant quantity and a Lyapunov function for convergence analysis of average-consensus problems on directed graphs. 
This Lyapunov function is a measure of group disagreement in the network. 
We show that a directed graph solves the average-consensus problem using a certain protocol if and only if it is balanced. 
Furthermore, we use properties of balanced networks to analyze the convergence of an agreement protocol for networks with switching topology. 
This variation of the network topology is usually due to link failures or creations in networks with mobile nodes. 
We introduce a common Lyapunov function that guarantees asymptotic convergence to a group decision value in a network with switching information ﬂow.

@@

Building on these basic results, we provide a number of extensions. 
We discuss the eﬀects of communication time-delays in solving consensus problems. 
For undirected graphs, we address average-consensus problem under the constraint that the inputs of all agents are bounded. 
This leads to analyzing a nonlinear protocol. 
Using a example of a network with three nodes, we demonstrate that analyzing the convergence of this protocol for general digraphs is a challenging open problem. 
Finally, we pose and address the max-consensus problem that is useful for determining a superior or leader in a group of agents in a distributed way.

@@

Simulation results are provided that demonstrate our theoretical predictions and show the novel analytical tools that we propose are eﬀective.

@@

An outline of this paper is as follows. 
In Section 2, we deﬁne consensus problems. 
In Section 3, we give two protocols. 
Some background on algebraic graph theory and properties of graph Laplacians are provided in Section 4. 
A counterexample is given in Section 5 that shows not every digraph solves an average-consensus problem. 
In Section 6, our main results on networks with switching topology are presented. 
Average-consensus problems for networks with communication time-delays is discussed in Section 7. 
In Section 8, our result on max-consensus problem is given. 
The simulation results are presented in Section 9. 
Finally, in Section 10, concluding remarks are stated.

@@

\section{Consensus Problems}
Let $G=(\mathcal{V},\mathcal{E},\mathcal{A})$ be a weighted directed graph (or digraph) with $n$ nodes and a weighted adjacency matrix $\mathcal{A}=[a_{ij}]$ where $a_{ij} \ge 0$ for all $i,j \in \mathcal{I}={1,2,…,n}$ with $i \ne j$. 
Here, $\mathcal{V}$ denotes the set of vertices $v_i$ and $\mathcal{E}$ denotes the set of edges $ij$ (or ($v_i,v_j$)) of the graph $G$. 
The set of neighbors of node $i$ is denoted by $N_i=\{ij\in \mathcal{E}:a_{ij}>0\}$. 
We call any subset of nodes $J$ a cluster. 
The set of neighbors of a cluster $J\subset \mathcal{I}$ is deﬁned by

@@

Let $x_i\in \mathbb{R}$ denote the value of node $i$. 
We refer to $G_x=(\mathcal{V},\mathcal{E},\mathcal{A},x)$ with $x=(x_1,...,x_n)^T$ as an algebraic graph or (static) network with value $x\in \mathbb{R}^n$ and information ﬂow $G=(\mathcal{V},\mathcal{E},\mathcal{A})$. 
The value of a node might represent physical quantities including attitude, position, temperature, voltage, and so on. 
We say nodes $i$ and $j$ in a network agree if and only $x_i=x_j$. 
We say all the nodes in a network have reached a consensus if and only if $x_i=x_j$ for all $i,j\in \mathcal{I}, i\ne j$. 
Whenever the nodes of a network are in agreement, the common value of all nodes is called the (group) decision value.

@@

Suppose each node of a graph is a dynamic agent with dynamics

假设图的每一个节点都是一个具有动态性能的动态智能体
\begin{equation}
    \dot{x}_i = f(x_i, u_i), i\in \mathcal{I}
    \tag{2}
    \label{2}
\end{equation}
A dynamic graph (or dynamic network) is deﬁned as a 4-tuple $G_{x(t)} = (\mathcal{V},\mathcal{E},\mathcal{A},x(t))$ together with dynamics $\dot{x}=F(x,u)$ where $x$ denotes the state of the dynamic graph and {\color{green}$F(x,u)$ is the column-wise concatenation of the elements $F_i(x,u)=f(x_i,u_i)$}.

@@

Let $\chi: \mathbb{R}^n \rightarrow \mathbb{R}$ be a function of $n$ variables $x_1,\dots,x_n$. 
The $\chi$-consensus problem in a dynamic graph is a distributed way to calculate $\chi(x(0))$ by applying inputs $u_i$ that only depend on the values of node $i$ and its neighbors. 
We say a protocol

定义$\chi: \mathbb{R}^n \rightarrow \mathbb{R}$是一个包含$n$个变量$x_1,\dots,x_n$的函数。
在一个动态图中的$\chi$-一致性问题，是通过利用输入$u_i$以一种分布式的方式来计算$\chi(x(0))$，其中输入$u_i$仅依赖于节点$i$的和它的邻居的值。
我们定义一个协议
\begin{equation}
    u_i = k_i(x_{j_1},\dots,x_{j_{m_i}})
    \tag{3}
    \label{3}
\end{equation}
with $j_1,\dots,j_{m_i}\in \{i\} \cup N_i$ and $m_i\leq n$ asymptotically solves the $\chi$ -consensus problem if and only if there exists an asymptotically stable equilibrium $x^*$ of $\dot{x}=F(x,k(x))$ such that $x^*=\chi(x(0))$ for all $i\in \mathcal{I}$. 
We are interested in solving the $\chi$ -consensus problem in a distributed fashion in which {\color{green}no node is connected to all other nodes (i.e. $m_i < n$ for all $i$)}.

@@

The special cases with $\chi(x)=Ave(x)=\frac{1}{n}(\sum_{i=1}^{n}x_i)$, $\chi(x)=Max(x)=\max_ix_i$ , and $\chi(x)=Min(x)=\min_ix_i$ are called average-consensus, max-consensus, and min-consensus, respectively due to their broad applications in distributed decision-making for multi-agent systems.

@@

% 最小一致性（min-consensus）
% $\chi(x)=Min(x)=min_ix_i$。
% }
Solving average-consensus problem is an example of distributed computation of a linear function $\chi(x)=Ave(x)$ using a network of dynamic systems. 
This is more challenging than just reaching a general agreement.

@@

\section{Consensus Protocols}
\noindent In this section, we present three consensus protocols that solve agreement problems in a network of continuous-time (CT) {\color{green}integrator agents} with dynamics

\noindent 这一部分，我们介绍了三种一致性协议，分别用来解决连续时间（continuous-time，CT）动态积分器智能体
\begin{equation}
    \dot{x}_i(t) = u_i(t)
    \tag{4}
    \label{4}
\end{equation}
% \begin{equation}
%     \text{\color{userColor}位置状态的一阶导数 = 输入}
%     \notag
% \end{equation}
\noindent or agents with discrete-time (DT) model

\noindent 和离散时间（discrete-time，DT）动态智能体模型的网络一致性问题，
\begin{equation}
    x_i(k+1) = x_i(k)+\epsilon u_i(k)
    \tag{5}
    \label{5}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{ 下一时刻的状态 = 此刻的状态 + }\epsilon \text{ * 此时的输入}
%     \notag
% \end{equation}
\noindent and step-size $\epsilon>0$. 
In this paper, we consider three scenarios:

@@

i) Fixed or switching topology and zero communication time-delay: We use the following linear consensus protocol:

i）固定或切换拓扑的零通信时延：我们使用下边的线性一致性协议：
\begin{equation}
    u_i = \sum_{j\in N_i}a_{ij}(x_j-x_i)
    \tag{A1}
    \label{A1}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{控制输入 = 对所有的\ 节点j和i的位置差值 * 两节点的权重\ 求和，其中j是所有i的邻居节点}
%     \notag
% \end{equation}

where the set of neighbors $N_i=N_i(G)$ of node $i$ is variable in networks with switching topology.

这里，节点$i$的邻居集合$N_i=N_i(G)$在切换拓扑网络中是一个变量。

ii) Fixed topology $G=(\mathcal{V}, \mathcal{E}, \mathcal{A})$ and communication time-delay $\tau_{ij}>0$ corresponding to the edge $ij\in \mathcal{E}$: We use the following linear time-delayed consensus protocol:

@@

The derivation of each of the aforementioned two protocols (A1) and (A2) becomes apparent during the convergence analysis that will be presented for each protocol later on. 
We show that in each case, consensus can is asymptotically reached. 
Moreover, we provide suﬃcient and necessary conditions on the directed information ﬂow in the network so that average-consensus, max-consensus, and min-consensus can be achieved. 
Furthermore, we provide results on performance and algorithmic robustness of these consensus protocols.

@@

\noindent{\em Remark} 1. For an undirected network with ﬁxed topology, both protocols solve the averageconsensus problem with appropriate technical conditions on delays. 
The challenge is to address similar consensus problems for networks with directed graphs and switching topology. 
In multi-agent ﬂocking [22], the information ﬂow is usually directed and the topology of the network goes through changes that are discrete-event type in the nature.

@@

Given Protocol (A1), the state of a network of continuous-time integrator agents evolves according to the following linear system

所给的协议（A1），连续时间网络的智能体状态会随着下面的线性系统进行变化
\begin{equation}
    \dot{x}(t) = -Lx(t) 
    \tag{6}
    \label{6}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{位置状态的一阶导数 = 拉普拉斯矩阵 * 位置状态值}
%     \notag
% \end{equation}
\noindent where L is called the graph Laplacian induced by the information ﬂow G and is deﬁned by

\noindent 这里，$L$是信息流网络$G$的图拉普拉斯矩阵，并且定义如下
\begin{equation}
l_{ij} = \left\{
    \begin{array}{ll}
        \sum_{k=1,k\ne i}^n a_{ik}, & j=i\\
        -a_{ij}, & j\ne i
    \end{array}\right.
    \tag{7}
    \label{7}
\end{equation}
\noindent The properties of graph Laplacian is one of the main areas of research in algebraic graph theory and is discussed in Section 4.

@@

% {\color{userColor} 关于图拉普拉斯的定义，还可查看文献[2013\_多智能体系统的协调控制研究综述-苗国英]
% 拉普拉斯矩阵定义为：$L=D-A$，
% $D$是度矩阵，$A$是邻接矩阵。
% }
In a network with switching topology, convergence analysis of Protocol (A1) is equivalent to stability analysis for a hybrid system

在一个切换拓扑（switching topology）网络中，协议(\ref{A1})的收敛性分析等价于混合系统（hybrid system）的稳定性分析
\begin{equation}
    \dot{x}(t) = -L_kx(t),\ k=s(t) 
    \tag{8}
    \label{8}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{位置状态的一阶导数 = 拉普拉斯矩阵（关于切换信号变换） * 位置状态值}
%     \notag
% \end{equation}
\noindent where $L_k = \mathcal{L}(G_k)$ is the Laplacian of $G_k$, $s(t)$ : $\mathbb{R}\rightarrow \mathcal{I} \subset \mathbb{Z}$ is a switching signal, and {\color{green}$\Gamma\ni G_k$ is a ﬁnite collection of digraphs (of order $n$) with the index set $\mathcal{I}_\Gamma$}. 
Later, we will see that $\Gamma$ is a relatively large set for $n\gg 1$. 
The task of stability analysis for the hybrid system in (8) is rather challenging partly because, in general, the product of two Laplacian matrices do not commute.

@@

For agents with discrete-time models, applying protocol (A1) gives the following discretetime network dynamics

对于离散时间的智能体模型，应用协议(\ref{A1})给出了如下的动态离散网络
\begin{equation}
    x(k+1) = P_\epsilon x(k)
    \tag{9}
    \label{9}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{ 下一时刻的状态 = 非负随机矩阵 * 此刻的状态}
%     \notag
% \end{equation}
\noindent with

@@

The convergence analysis of Protocol (A1) for discrete-time agents heavily relies on the theory of nonnegative matrices [10, 12, 16] and will be discussed in a separate paper. 
Our approach presents a Lyapunov-based convergence analysis for agreement in networks with discrete-time models. 
This is diﬀerent than the approach pursued in the work by Jadbabaie et al. which strongly relies on matrix theoretic properties and {\color{green}inﬁnite right-convergent products (RCP) of stochastic matrices [2, 3]}.

@@

\section{Algebraic Graph Theory: Properties of Laplacians}
在这一部分，我们介绍图论的基本的概念和标记，这些知识都将在文章的后边被用到。
更多的信息参考文献[11,5]。
更加复杂全面的关于无向图的拉普拉斯算子请参考文献[17]。
然而，我们需要用到的关于无向图的拉普拉斯的基本概念无法在图论的书籍文献中找到，因此我们罗列在这里。

定义$G=(\mathcal{V}, \mathcal{E}, \mathcal{A})$为一个加权有向图（或有向图），具有$n$个节点。
节点$v_i$的入度（in-degree）和出度（out-degree）分别定义如下：
\begin{equation}
    \deg_{in}(v_i) = \sum_{j=1}^{n}a_{ji},\quad \deg_{out}(v_i) = \sum_{j=1}^{n}a_{ij}
    \tag{11}
    \label{11}
\end{equation}

>>>>

\geometry{a4paper,scale=0.8}
\geometry{a4paper,left=3.18cm,right=3.18cm,top=2.54cm,bottom=2.54cm}
\linespread{1.5}
% \setlength{\parskip}{0.5\baselineskip} % 段落间距

@@

\begin{abstract}
{\color[gray]{0.5}
In this paper, we discuss consensus problems for a network of dynamic agents with ﬁxed and switching topologies. 
We analyze three cases: i) networks with switching topology and no time-delays, ii) networks with ﬁxed topology and communication time-delays, and iii) max-consensus problems (or leader determination) for groups of discrete-time agents. 
In each case, we introduce a linear/nonlinear consensus protocol and provide convergence analysis for the proposed distributed algorithm. 
Moreover, we establish a connection between the Fiedler eigenvalue of the information ﬂow in a network (i.e. algebraic connectivity of the network) and the negotiation speed (or performance) of the corresponding agreement protocol. 
It turns out that balanced digraphs play an important role in addressing average-consensus problems. 
We introduce disagreement functions that play the role of Lyapunov functions in convergence analysis of consensus protocols. 
A distinctive feature of this work is to address consensus problems for networks with directed information ﬂow. 
We provide analytical tools that rely on algebraic graph theory, matrix theory, and control theory. 
Simulations are provided that demonstrate the eﬀectiveness of our theoretical results.
}

@@

\section{Introduction}
{\color[gray]{0.5}
Distributed decision-making for coordination of networks of dynamic agents has attracted several researchers in recent years. 
This is partly due to broad applications of multi-agent systems in many areas including cooperative control of unmanned air vehicles (UAVs), ﬂocking of birds [22, 24, 23], schooling for underwater vehicles, distributed sensory networks, attitude alignment of clusters of satellites, and congestion control in communication networks [21].
}

@@

{\color[gray]{0.5}
Agreement problems have a long history in the ﬁeld of computer science, particularly in automata theory and distributed computation [15]. 
In many applications involving multiagent/multi-vehicle systems, groups of agents need to agree upon certain quantities of {\color{green}interest}. 
Such quantities might or might not be related to the motion of the individual agents. 
As a result, it is important to address agreement problems in their general form for networks of dynamic agents with directed information ﬂow under link failure and creation (i.e. variable network topology).
}

@@

{\color[gray]{0.5}
Our main contribution in this paper is to deﬁne and address consensus problems under a variety of assumptions on the network topology (being ﬁxed or variable), presence or lack of communication time-delays, and boundedness of the inputs of dynamic agents. 
In each case, we provide convergence analysis and for linear protocols establish direct connections between performance and robustness of a consensus protocol and the properties of graph Laplacian of the information ﬂow in the network.
}

@@

{\color[gray]{0.5}
In the past, a number of researchers have worked in problems that are essentially diﬀerent forms of agreement problems with diﬀerences regarding the types of agent dynamics, the properties of the graphs, and {\color{green}the names of the tasks of interest}. 
In [25, 7, 6], graph Laplacians are used for the task of formation stabilization for groups of agents with linear dynamics. 
Their method for formation stabilization has not yet been extended to systems with nonlinear dynamics that are not feedback linearizable. 
Special cases of this approach are known as leader-follower type architectures and have been widely used by numerous researchers [19, 4, 14]. 
In [18], graph Laplacians are used in the context of dynamic graph theory. 
In [24, 23], {\color{green}ﬂocking and heading angle} alignment for multiple particles is analyzed from the point of view of statistical mechanics and a phase transition phenomenon is observed that occurs the information ﬂow in the network becomes connected. 
The work in [13] focuses on attitude alignment for undirected graphs in which the agents have simple dynamics motivated by the model used in [24]. 
It is claimed that the connectivity of the graph on average is suﬃcient for convergence of the heading angles of the agents. 
In [20], the authors addressed convergence of linear and nonlinear protocols for networks with undirected graphs in presence or lack of communication time-delays. 
Theoretically, analyzing consensus on directed graphs is more challenging and is considered in the present paper.
}

@@

{\color[gray]{0.5}
In this paper, we provide convergence analysis of consensus protocol for a network of {\color{green}integrators} with a directed information ﬂow and ﬁxed or switching topology. 
Our analysis relies on several tools from algebraic graph theory [1, 11] and matrix theory [12]. 
We establish a connection between the performance of the linear consensus protocol and the Fiedler eigenvalue of graph Laplacian of a graph called the mirror graph (that is closely-related to the original directed graph).
}

@@

{\color[gray]{0.5}
It turns out that a class of directed graphs called balanced graphs have a crucial role in derivation of an invariant quantity and a Lyapunov function for convergence analysis of average-consensus problems on directed graphs. 
This Lyapunov function is a measure of group disagreement in the network. 
We show that a directed graph solves the average-consensus problem using a certain protocol if and only if it is balanced. 
Furthermore, we use properties of balanced networks to analyze the convergence of an agreement protocol for networks with switching topology. 
This variation of the network topology is usually due to link failures or creations in networks with mobile nodes. 
We introduce a common Lyapunov function that guarantees asymptotic convergence to a group decision value in a network with switching information ﬂow.
}

@@

{\color[gray]{0.5}
Building on these basic results, we provide a number of extensions. 
We discuss the eﬀects of communication time-delays in solving consensus problems. 
For undirected graphs, we address average-consensus problem under the constraint that the inputs of all agents are bounded. 
This leads to analyzing a nonlinear protocol. 
Using a example of a network with three nodes, we demonstrate that analyzing the convergence of this protocol for general digraphs is a challenging open problem. 
Finally, we pose and address the max-consensus problem that is useful for determining a superior or leader in a group of agents in a distributed way.
}

@@

{\color[gray]{0.5}
Simulation results are provided that demonstrate our theoretical predictions and show the novel analytical tools that we propose are eﬀective.
}

@@

{\color[gray]{0.5}
An outline of this paper is as follows. 
In Section 2, we deﬁne consensus problems. 
In Section 3, we give two protocols. 
Some background on algebraic graph theory and properties of graph Laplacians are provided in Section 4. 
A counterexample is given in Section 5 that shows not every digraph solves an average-consensus problem. 
In Section 6, our main results on networks with switching topology are presented. 
Average-consensus problems for networks with communication time-delays is discussed in Section 7. 
In Section 8, our result on max-consensus problem is given. 
The simulation results are presented in Section 9. 
Finally, in Section 10, concluding remarks are stated.
}

@@

\section{Consensus Problems}
{\color[gray]{0.5}
Let $G=(\mathcal{V},\mathcal{E},\mathcal{A})$ be a weighted directed graph (or digraph) with $n$ nodes and a weighted adjacency matrix $\mathcal{A}=[a_{ij}]$ where $a_{ij} \ge 0$ for all $i,j \in \mathcal{I}={1,2,…,n}$ with $i \ne j$. 
Here, $\mathcal{V}$ denotes the set of vertices $v_i$ and $\mathcal{E}$ denotes the set of edges $ij$ (or ($v_i,v_j$)) of the graph $G$. 
The set of neighbors of node $i$ is denoted by $N_i=\{ij\in \mathcal{E}:a_{ij}>0\}$. 
We call any subset of nodes $J$ a cluster. 
The set of neighbors of a cluster $J\subset \mathcal{I}$ is deﬁned by
}

@@

{\color[gray]{0.5}
Let $x_i\in \mathbb{R}$ denote the value of node $i$. 
We refer to $G_x=(\mathcal{V},\mathcal{E},\mathcal{A},x)$ with $x=(x_1,...,x_n)^T$ as an algebraic graph or (static) network with value $x\in \mathbb{R}^n$ and information ﬂow $G=(\mathcal{V},\mathcal{E},\mathcal{A})$. 
The value of a node might represent physical quantities including attitude, position, temperature, voltage, and so on. 
We say nodes $i$ and $j$ in a network agree if and only $x_i=x_j$. 
We say all the nodes in a network have reached a consensus if and only if $x_i=x_j$ for all $i,j\in \mathcal{I}, i\ne j$. 
Whenever the nodes of a network are in agreement, the common value of all nodes is called the (group) decision value.
}

@@

{\color[gray]{0.5}
Suppose each node of a graph is a dynamic agent with dynamics
}

假设图的每一个节点都是一个具有动态性能的动态智能体
\begin{equation}
    \dot{x}_i = f(x_i, u_i), i\in \mathcal{I}
    \tag{2}
    \label{2}
\end{equation}
{\color[gray]{0.5}
\noindent A dynamic graph (or dynamic network) is deﬁned as a 4-tuple $G_{x(t)} = (\mathcal{V},\mathcal{E},\mathcal{A},x(t))$ together with dynamics $\dot{x}=F(x,u)$ where $x$ denotes the state of the dynamic graph and {\color{green}$F(x,u)$ is the column-wise concatenation of the elements $F_i(x,u)=f(x_i,u_i)$}.
}

@@

{\color[gray]{0.5}
Let $\chi: \mathbb{R}^n \rightarrow \mathbb{R}$ be a function of $n$ variables $x_1,\dots,x_n$. 
The $\chi$-consensus problem in a dynamic graph is a distributed way to calculate $\chi(x(0))$ by applying inputs $u_i$ that only depend on the values of node $i$ and its neighbors. 
We say a protocol
}

定义$\chi: \mathbb{R}^n \rightarrow \mathbb{R}$是一个包含$n$个变量$x_1,\dots,x_n$的函数。
在一个动态图中的$\chi$-一致性问题，是通过利用输入$u_i$以一种分布式的方式来计算$\chi(x(0))$，其中输入$u_i$仅依赖于节点$i$的和它的邻居的值。
我们定义一个协议
\begin{equation}
    u_i = k_i(x_{j_1},\dots,x_{j_{m_i}})
    \tag{3}
    \label{3}
\end{equation}
{\color[gray]{0.5}
\noindent with $j_1,\dots,j_{m_i}\in \{i\} \cup N_i$ and $m_i\leq n$ asymptotically solves the $\chi$ -consensus problem if and only if there exists an asymptotically stable equilibrium $x^*$ of $\dot{x}=F(x,k(x))$ such that $x^*=\chi(x(0))$ for all $i\in \mathcal{I}$. 
We are interested in solving the $\chi$ -consensus problem in a distributed fashion in which {\color{green}no node is connected to all other nodes (i.e. $m_i < n$ for all $i$)}.
}

@@

{\color[gray]{0.5}
The special cases with $\chi(x)=Ave(x)=\frac{1}{n}(\sum_{i=1}^{n}x_i)$, $\chi(x)=Max(x)=\max_ix_i$ , and $\chi(x)=Min(x)=\min_ix_i$ are called average-consensus, max-consensus, and min-consensus, respectively due to their broad applications in distributed decision-making for multi-agent systems.
}

@@

% 最小一致性（min-consensus）
% $\chi(x)=Min(x)=min_ix_i$。
% }
{\color[gray]{0.5}
Solving average-consensus problem is an example of distributed computation of a linear function $\chi(x)=Ave(x)$ using a network of dynamic systems. 
This is more challenging than just reaching a general agreement.
}

@@

\section{Consensus Protocols}
{\color[gray]{0.5}
\noindent In this section, we present three consensus protocols that solve agreement problems in a network of continuous-time (CT) {\color{green}integrator agents} with dynamics
}

\noindent 这一部分，我们介绍了三种一致性协议，分别用来解决连续时间（continuous-time，CT）动态积分器智能体
\begin{equation}
    \dot{x}_i(t) = u_i(t)
    \tag{4}
    \label{4}
\end{equation}
% \begin{equation}
%     \text{\color{userColor}位置状态的一阶导数 = 输入}
%     \notag
% \end{equation}
{\color[gray]{0.5}
\noindent or agents with discrete-time (DT) model
}

\noindent 和离散时间（discrete-time，DT）动态智能体模型的网络一致性问题，
\begin{equation}
    x_i(k+1) = x_i(k)+\epsilon u_i(k)
    \tag{5}
    \label{5}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{ 下一时刻的状态 = 此刻的状态 + }\epsilon \text{ * 此时的输入}
%     \notag
% \end{equation}
{\color[gray]{0.5}
\noindent and step-size $\epsilon>0$. 
In this paper, we consider three scenarios:
}

@@

{\color[gray]{0.5}
i) Fixed or switching topology and zero communication time-delay: We use the following linear consensus protocol:
}

i）固定或切换拓扑的零通信时延：我们使用下边的线性一致性协议：
\begin{equation}
    u_i = \sum_{j\in N_i}a_{ij}(x_j-x_i)
    \tag{A1}
    \label{A1}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{控制输入 = 对所有的\ 节点j和i的位置差值 * 两节点的权重\ 求和，其中j是所有i的邻居节点}
%     \notag
% \end{equation}
{\color[gray]{0.5}
\noindent where the set of neighbors $N_i=N_i(G)$ of node $i$ is variable in networks with switching topology.
}

\noindent 这里，节点$i$的邻居集合$N_i=N_i(G)$在切换拓扑网络中是一个变量。

{\color[gray]{0.5}
ii) Fixed topology $G=(\mathcal{V}, \mathcal{E}, \mathcal{A})$ and communication time-delay $\tau_{ij}>0$ corresponding to the edge $ij\in \mathcal{E}$: We use the following linear time-delayed consensus protocol:
}

@@

{\color[gray]{0.5}
The derivation of each of the aforementioned two protocols (A1) and (A2) becomes apparent during the convergence analysis that will be presented for each protocol later on. 
We show that in each case, consensus can is asymptotically reached. 
Moreover, we provide suﬃcient and necessary conditions on the directed information ﬂow in the network so that average-consensus, max-consensus, and min-consensus can be achieved. 
Furthermore, we provide results on performance and algorithmic robustness of these consensus protocols.
}

@@

{\color[gray]{0.5}
\noindent{\em Remark} 1. For an undirected network with ﬁxed topology, both protocols solve the averageconsensus problem with appropriate technical conditions on delays. 
The challenge is to address similar consensus problems for networks with directed graphs and switching topology. 
In multi-agent ﬂocking [22], the information ﬂow is usually directed and the topology of the network goes through changes that are discrete-event type in the nature.
}

@@

{\color[gray]{0.5}
Given Protocol (A1), the state of a network of continuous-time integrator agents evolves according to the following linear system
}

所给的协议（A1），连续时间网络的智能体状态会随着下面的线性系统进行变化
\begin{equation}
    \dot{x}(t) = -Lx(t) 
    \tag{6}
    \label{6}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{位置状态的一阶导数 = 拉普拉斯矩阵 * 位置状态值}
%     \notag
% \end{equation}
{\color[gray]{0.5}
\noindent where L is called the graph Laplacian induced by the information ﬂow G and is deﬁned by
}

\noindent 这里，$L$是信息流网络$G$的图拉普拉斯矩阵，并且定义如下
\begin{equation}
l_{ij} = \left\{
    \begin{array}{ll}
        \sum_{k=1,k\ne i}^n a_{ik}, & j=i\\
        -a_{ij}, & j\ne i
    \end{array}\right.
    \tag{7}
    \label{7}
\end{equation}
{\color[gray]{0.5}
\noindent The properties of graph Laplacian is one of the main areas of research in algebraic graph theory and is discussed in Section 4.
}

@@

% {\color{userColor} 关于图拉普拉斯的定义，还可查看文献[2013\_多智能体系统的协调控制研究综述-苗国英]
% 拉普拉斯矩阵定义为：$L=D-A$，
% $D$是度矩阵，$A$是邻接矩阵。
% }
{\color[gray]{0.5}
In a network with switching topology, convergence analysis of Protocol (A1) is equivalent to stability analysis for a hybrid system
}

在一个切换拓扑（switching topology）网络中，协议(\ref{A1})的收敛性分析等价于混合系统（hybrid system）的稳定性分析
\begin{equation}
    \dot{x}(t) = -L_kx(t),\ k=s(t) 
    \tag{8}
    \label{8}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{位置状态的一阶导数 = 拉普拉斯矩阵（关于切换信号变换） * 位置状态值}
%     \notag
% \end{equation}
{\color[gray]{0.5}
\noindent where $L_k = \mathcal{L}(G_k)$ is the Laplacian of $G_k$, $s(t)$ : $\mathbb{R}\rightarrow \mathcal{I} \subset \mathbb{Z}$ is a switching signal, and {\color{green}$\Gamma\ni G_k$ is a ﬁnite collection of digraphs (of order $n$) with the index set $\mathcal{I}_\Gamma$}. 
Later, we will see that $\Gamma$ is a relatively large set for $n\gg 1$. 
The task of stability analysis for the hybrid system in (8) is rather challenging partly because, in general, the product of two Laplacian matrices do not commute.
}

@@

{\color[gray]{0.5}
For agents with discrete-time models, applying protocol (A1) gives the following discretetime network dynamics
}

对于离散时间的智能体模型，应用协议(\ref{A1})给出了如下的动态离散网络
\begin{equation}
    x(k+1) = P_\epsilon x(k)
    \tag{9}
    \label{9}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{ 下一时刻的状态 = 非负随机矩阵 * 此刻的状态}
%     \notag
% \end{equation}

{\color[gray]{0.5}
\noindent with
}

@@

{\color[gray]{0.5}
The convergence analysis of Protocol (A1) for discrete-time agents heavily relies on the theory of nonnegative matrices [10, 12, 16] and will be discussed in a separate paper. 
Our approach presents a Lyapunov-based convergence analysis for agreement in networks with discrete-time models. 
This is diﬀerent than the approach pursued in the work by Jadbabaie et al. which strongly relies on matrix theoretic properties and {\color{green}inﬁnite right-convergent products (RCP) of stochastic matrices [2, 3]}.
}

@@

\section{Algebraic Graph Theory: Properties of Laplacians}
{\color[gray]{0.5}
\noindent In this section, we introduce some basic concepts and notation in graph theory that will be used throughout the paper. 
More information is available in [11, 5]. 
A comprehensive survey on properties of Laplacians of undirected graphs can be found in [17]. 
However, we need to work with Laplacians of directed graphs that the basic properties cannot be found in graph theory literature and will be stated here.
}

\noindent 在这一部分，我们介绍了一些图论的基本概念和注解，这些知识都将在文章的后边被用到。
更多的信息请参考文献[11,5]。
更加复杂全面的关于无向图的拉普拉斯矩阵研究请参考文献[17]。
然而，我们需要用到的关于无向图的拉普拉斯矩阵的基本概念无法在图论的文献中找到，因此我们罗列在这里。

{\color[gray]{0.5}
Let $G=(\mathcal{V}, \mathcal{E}, \mathcal{A})$ be a weighted directed graph (or digraph) with $n$ nodes. 
The in-degree and out-degree of node $v_i$ are, respectively, deﬁned as follows:
}

定义$G=(\mathcal{V}, \mathcal{E}, \mathcal{A})$为一个具有$n$个节点的加权有向图（或有向图）。
节点$v_i$的入度和出度分别定义如下：
